\input{../style.tex}

\title{BlackBoard log}
\what{}
\supervisors{}
\author{Tom van Duist}
\date{Oktober 30, 2015}


\begin{document}

\maketitle



\clearpage

\chapter{Personal BlackBoard use}
Personally I avoid BlackBoard whenever I can as I find it cumbersome to work with. To this end I mainly come to BlackBoard to download the available content so I can save it locally and synchronize it with all my devices using Dropbox, in this way it is also easy to view the files with a smartphone.

I will aggregate the way in which I use BlackBoard as a list of actions that I perform. From these I will draw a couple of conclusions and observations.


\section{BlackBoard log}

\textbf{Download files:}
\begin{enumerate}
	\item Go to the relevant course.
	\item Click on 'Course Materials'.
	\item Look for any new files and download them.
	\item Repeat step 2 and 3 for the sections 'Assignments', 'Course Information' and 'Announcements'.
	\item Synchronize files using Dropbox.
\end{enumerate}

\textbf{Hand in assignment:}
\begin{enumerate}
	\item Go to relevant course.
	\item Click on 'Assignments'.
	\item Click on relevant assignment title.
	\item Click on continue in the bottom right corner.
	\item Find the upload or browse button and upload the file.
	\item Click submit (this will automatically show the created submission).
	\item Double check if it is the correct file by downloading the submission by clicking the download button next to the file.
\end{enumerate}

\pagebreak[4]

\textbf{Read announcements:}
\begin{enumerate}
	\item Go to relevant course.
	\item Click on 'Announcements'.
	\item Read if there are any new announcements.
	\item Go to step 1 for every active course.
\end{enumerate}

\textbf{View grades:}
\begin{enumerate}
	\item Go to relevant course.
	\item Either click on 'Assignments":
	\begin{enumerate}
		\item Click on the title of the relevant assignment.
		\item Look if the grade has been updated on the right.
	\end{enumerate}
	\item Or click on 'Tools':
	\begin{enumerate}
		\item Click on 'My Gradees'.
		\item View if the grade has been updated for the relevant section.
	\end{enumerate}
\end{enumerate}


\section{Observations}

\begin{itemize}
	\item Most actions, such as viewing a grade or reading an announcements are initiated once I learn of new developments through other communication channels.
	\item Handing in an assignment was very confusing the first time and we ended up uploading it at a wrong location.
\end{itemize}


\section{Conclusions}

\begin{itemize}
	\item The process of handing in an assignment is confusing.
	\item Two ways of viewing grades is confusing.
	\item It is too cumbersome to view files, making it easier to download them to bypass BlackBoard afterwards.
	\item Every course has a different way to organize the content so you are always searching for what you need.
	\item Getting emails or other notifications outside BlackBoard about grades and announcements would be a good feature.
	\item General page on BlackBoard with contact information about teachers instead of finding it inside the course would be convenient.
\end{itemize}


\chapter{Reading assignments}

\section*{1.1}

\begin{itemize}
	\item BlackBoard itself.
	\item Statistics about the use of BlackBoard.
	\item Similar learning management tools.
	\item Stakeholders (students, teachers).
	\item Tools used at other universities.
	\item New developments and trends.
\end{itemize}


\section*{1.2}

\begin{enumerate}
	\item Does the current tool meet the business goals?
	\item What were the requirements for the current system?
	\item What are the priorities of the different business goals and requirements?
\end{enumerate}


\end{document}
